Bayesian Exploration in Deep Reinforcement Learning

### 2022-02-08 papers/main.tex
Priors

\subsection{Noisy Networks}
NoisyNet can be viewed as a stochastic
process represented by a neural network with stochastic weights. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(\rho_\phi\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
out that for the mean squared error loss in DQN, there always exsists a deterministic
optimal policy. They show through emipirical analysis, however, that this does not
mean that the policy necessarily disregards the noise and converges to a deterministic
policy.

@@

Now the stochastic processes is represented by a neural network \(\rho_\phi\) and a prior \(p\). In a similar
manner to NoisyNet, we sample a function \(f\) from \(\rho_\phi\) by sampling a random noise vector
\(\xi\), and then defining \(f(\bm{x}) = g_\phi(\bm{x}, \xi)\). They further show that the
gradient of the KL-divergence for functions evaluated at the measurement set \(\X\) is

@@

The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
in the space of interesting test cases.

@@

We can use the functional variational Bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(k\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \lambda \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^\mathbf{M}\) is \(f\) applied to
a set of i.i.d. random points \(\mathbf{M} = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let the measurement \(\mathbf{M}\) be the the set of all state-action
pairs for states we have already explored. If the MDP is ergodic, then \(\textbf{M}\) will eventually
have full support in \(\state \times \action\).

@@

\subsection{Informative Prior}
One of the benefits of a functional prior is that we can incorporate domain knowledge to
get more efficient exploration. We will now look at how our method can utilize domain
knowledge to improve sample efficiency.

>>>>

\subsection{Noisy Networks}
NoisyNet can be viewed as a stochastic
process represented by a neural network with stochastic weights. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(\rho_\phi\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
out that for the mean squared error loss in DQN, there always exsists a deterministic
optimal policy. They show through emipirical analysis, however, that this does not
mean that the policy necessarily converges to a deterministic policy.

@@

We will use this identity to approximate the functional KL-divergence by sampling 
measurement sets \(\X \in \mathcal{X}^n\). Note that because this KL-divergence is a 
supremum, sampling measurment sets will always give us an underestimate of the true
KL-divergence.

In our case \(\mathcal{X} = \state \times \action\). First we start by
defining \(\X^D\) as the set of datapoints \(\D \in \state \times \action\) that we have
explored, but we also need points outside of what we have already explored. Sampling points
from undiscovered states is difficult, however, since we typically don't know what the set
of possible states includes. Since we know that each state only supports a finite number of
actions, we propose to let \(\X^M\) be a set of state-action pairs that 
The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
in the space of interesting test cases.

Now the stochastic processes is represented by a neural network \(g_\phi\) with sampling
distribution \(\rho_\phi\) and a prior \(p\). In a similar
manner to NoisyNet, we sample a function \(f\) from \(\rho_\phi\) by sampling a random noise vector
\(\xi\), and then defining \(f(\bm{x}) = g_\phi(\bm{x}, \xi)\). They further show that the
gradient of the KL-divergence for functions evaluated at the measurement set \(\X\) is

@@

@@

We can use the functional variational Bayesian neural
network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
NoisyNet uses one sample from Q for each optimization step. We will instead use
\(k\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
encourages stochasticity.
The maximization target becomes:
\begin{equation}
    \log p(\D_\omega^N \vert f) - \lambda \KL \left[ q(\f(\D_\omega^N), \f(\mathbf{M})) \Vert p(\f({\D_\omega^N}), \f(\mathbf{M})) \right],
\end{equation}
where \(\f({\D_\omega^N})\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f(\mathbf{M})\) is \(f\) applied to
a set of i.i.d. random points \(\mathbf{M} = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let the measurement \(\mathbf{M}\) be the the set of all state-action
pairs for states we have already explored. If the MDP is ergodic, then \(\textbf{M}\) will eventually
have full support in \(\state \times \action\).

@@

\subsection{Informative Prior}
One of the benefits of a functional prior is that we can incorporate domain knowledge to
get more efficient exploration. We will now look at how our method can utilize domain
knowledge to improve sample efficiency. To measure the effectiveness of priors we will use
a distribution that has a higher concentration of large Q-values for actions that we want
to incentivize.
